Data Preparation

### 2019-01-10 Data Preparation.Rmd
Deletes renaming variables section and adds text to Selecting Variables section

###Renaming Variables
First we rename the variable names to make them more comprehensible:
```{r}

###Identifying usless variables
Our dataframe contains many variables that are either empty or meaningless for our analysis. We identify this variables and save them to a vector to remove at a later stage.

NOTE TO RAPHAEL: This was in case we later wanted to use any of the non-empty variables, but I don't think we need this anymore, so you can safely just cut this section and select fewer variables later. 
```{r}
d_transcript <- d_transcript %>%
  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
         `Program (Description)`, `Academic Year`, `Academic Session`,
         `Appraisal (Description)`,
         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
  rename(`Student ID Number` = `Student Number`,
         `Course Code` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         `Civil Year` = `Academic Year`, # double check
         `Period` = `Academic Session`,
         `Appraisal` = `Appraisal (Description)`, # is there a better name for the variable?
         `Number Repeated Attempt` = `Number rep. attemp`,
         `Grade` = `Grade symbol`,
         `Status` = `Booking Status (Desc.)`) # is there a better name for the variable?
```

>>>>

###Selecting Variables

Our dataframe contains many variables that are either empty or meaningless for our analysis, thus we select ony the 10 variables that we will use for the anlysis, and give them more comprehensible names.

```{r}
d_transcript <- d_transcript %>%
  select(`Student Number`, `Module (Abbrev.)`, `Module (Desc.)`,
         `Program (Description)`, `Academic Year`, `Academic Session`,
         `Appraisal (Description)`,
         `Number rep. attemp`, `Grade symbol`, `Booking Status (Desc.)`) %>%
  rename(`Student ID Number` = `Student Number`,
         `Course Code` = `Module (Abbrev.)`,
         `Course Title` = `Module (Desc.)`,
         `Study Program` = `Program (Description)`,
         `Civil Year` = `Academic Year`, # double check
         `Period` = `Academic Session`,
         `Appraisal` = `Appraisal (Description)`, # is there a better name for the variable?
         `Number Repeated Attempt` = `Number rep. attemp`,
         `Grade` = `Grade symbol`,
         `Status` = `Booking Status (Desc.)`) # is there a better name for the variable?
```
